Demystifying the Combination of Dynamic Slicing and \\ Spectrum-based Fault Localization

### 2019-05-12 paper/ijcai/paper.tex
added link to the tool + theorem1 -> claim 1 fixed

\documentclass{article}
\pdfpagewidth=8.5in
\pdfpageheight=11in
\usepackage{ijcai19}
% The file ijcai18.sty is the style file for IJCAI-18 (same as ijcai08.sty).

@@

\hypersetup{draft}
\begin{document}

@@

Our implementation of Critical Slicing is based on the Mozilla Lithium
tool\footnote{Lithium details available at {\footnotesize\url{https://github.com/MozillaSecurity/lithium}} (Accessed \today)}. It takes as input a file
and produces as output a simplified version of that file that
satisfies a user-defined oracle. In our case, the oracle is defined
such that the test produces the same failure manifestation as the one
observed with the test execution on the original program. The
Lithium minimization process starts by determining the initial size---in
number of lines---of chunks to delete from the input file. For that,
it chooses the highest power of two number smaller than the file
size. For example, if the file has $1,000$ lines, Lithium sets the
initial chunk size to $512$ lines. Then, the tool starts a local search looking
for chunks to exclude from the file. If the chunk satisfies the oracle it is removed.
When no more chunks of that given size can be removed, Lithium
divides the chunk size by two and repeats the search. This iterative
process continues until no more lines can be removed.  If $n$ is the
size of the input file and $m$ is the size of the 1-minimal file found
by Lithium, then Lithium usually performs $O(m\cdot\lg(n))$
iterations. Proofs of the algorithm complexity can be found
elsewhere\footnote{Lithium complexity available at \url{https://github.com/MozillaSecurity/lithium/blob/master/src/lithium/docs/algorithm.md} (Accessed \today)}. Our implementation is publicly
available at \textit{$<$anonymized for double-blind review$>$}.

\begin{theorem}\label{the:1}
  The faulty statement may not be included in the critical slice of
  failing test cases.
\end{theorem}

@@

\begin{theorem}
  The rank of faulty statements cannot decrease if the slice includes
  the faulty statements.
\end{theorem}

@@

The first question evaluates the ability of dynamic slicing to reduce
the size of application code. Improvements on fault localization
depend on that ability. The second question addresses the problem that
affects all dynamic slicing
techniques~\cite{Lin:2018:BDE:3238147.3238163}---that of missing
faulty statements (see Theorem~\ref{the:1}). Developers would
not be able to successfully debug code for the cases that issue is
manifested. The third research question evaluates the impact of the
combination, as substantiated by \comb, to fault localization.

>>>>

\documentclass{article}
\pdfpagewidth=8.5in
\pdfpageheight=11in
\usepackage{ijcai19}

@@

%\hypersetup{draft}
\begin{document}

@@

Our implementation of Critical Slicing is based on the Mozilla Lithium
tool\footnote{Lithium details available at {\footnotesize\url{https://github.com/MozillaSecurity/lithium}} (Accessed \today)}. It takes as input a file
and produces as output a simplified version of that file that
satisfies a user-defined oracle. In our case, the oracle is defined
such that the test produces the same failure manifestation as the one
observed with the test execution on the original program. The
Lithium minimization process starts by determining the initial size---in
number of lines---of chunks to delete from the input file. For that,
it chooses the highest power of two number smaller than the file
size. For example, if the file has $1,000$ lines, Lithium sets the
initial chunk size to $512$ lines. Then, the tool starts a local search looking
for chunks to exclude from the file. If the chunk satisfies the oracle it is removed.
When no more chunks of that given size can be removed, Lithium
divides the chunk size by two and repeats the search. This iterative
process continues until no more lines can be removed.  If $n$ is the
size of the input file and $m$ is the size of the 1-minimal file found
by Lithium, then Lithium usually performs $O(m\cdot\lg(n))$
iterations. Proofs of the algorithm complexity can be found
elsewhere\footnote{Lithium complexity available at \url{https://github.com/MozillaSecurity/lithium/blob/master/src/lithium/docs/algorithm.md} 
(Accessed \today)}. Our implementation is publicly available at 
\url{https://github.com/damorim/lithium-slicer}.

\begin{namedthm}{Claim}\label{claim:1}
  The faulty statement may not be included in the critical slice of
  failing test cases.
\end{namedthm}

@@

\begin{namedthm}{Claim}\label{claim:2}
  The rank of faulty statements cannot decrease if the slice includes
  the faulty statements.
\end{namedthm}

@@

The first question evaluates the ability of dynamic slicing to reduce
the size of application code. Improvements on fault localization
depend on that ability. The second question addresses the problem that
affects all dynamic slicing
techniques~\cite{Lin:2018:BDE:3238147.3238163}---that of missing
faulty statements (see Claim~\ref{claim:1}). Developers would
not be able to successfully debug code for the cases that issue is
manifested. The third research question evaluates the impact of the
combination, as substantiated by \comb, to fault localization.
